Continuous Models for Scene and Traffic Participant Interactions in Road Scene Understanding.

### 2015-01-29 Paper/supplementary.tex
Added supplementary.tex

\begin{comment}
  Consider that we have a set of measurements whose mean and variance are known $\mu = E(x)$ and $\Sigma = E ((x - \mu_x)(x - \mu_x)^\top)$. We want to know the
  affect of uncertainty on mean and variance of existing observations. On adding
  noise $[\Delta x, \Delta y]^\top$ with zero mean and covariance $\Delta
  \Sigma = E(\Delta x \Delta x^\top)$ the covariance of new data is given by
  \begin{multline}
    E((x + \Delta x)(x+\Delta x)^\top) = E(xx^\top) + E(x \Delta x^\top) \\
    + E(\Delta x x^\top) + E(\Delta x \Delta x^\top)
  \end{multline}
  where the terms $E(x \Delta x^\top)$ denote the correlation between the data
  vector and the uncertainty in the data. Although we understand that in our case
  the data is the appearance based detection score and uncertainty because of
  occlusion is closely related to the appearance and hence detection score, we
  assume independence between $x$ and $\Delta x$. Hence our resultant covariance
  matrix $ E((x + \Delta x)(x+\Delta x)^\top) = \Sigma + \Delta \Sigma$
  are 4D. But that should not be a problem because the detection scores are
  modeled as $[x_{\text{min}}, y_{\text{min}}, x_{\text{max}},
  y_{\text{max}}]^\top$, we can stack the vectors in the soft occlusion region
  domain as the regions are independent of min or max variation. The parameters
  of 4D occlusion distribution are given by

@@

  With our
  discussion so far, the function $O_{ij}(.)$ gives an additional measure of
  uncertainty associated with each point in the space.
\end{comment}

@@

  %%%%%%%%%%%%%%%% Analytical attempt to integration %%%%%%%%%%%%%%%%%%%%%
  \begin{align}

    E^i_{\text{reproj}}(\lambda) &= \left\|\trackpj{t} - \frac{p_{1:2}\lambda +
  q_{1:2}}{p_3\lambda + q_3}\right\|^2\\
  &= \frac{(p_1\lambda + q_1 - u_{j1}(t))^2 + (p_2\lambda + q_2 - u_{j2}(t))^2}
  {(p_3\lambda + q_3)^2}\\
  &= \frac{a\lambda^2 + b\lambda + c}{(p_3\lambda + q_3)^2}
  \end{align}
  where $a = p_1^2 + p_2^2$, $b = 2p_1(q_1 - u_{j1}(t)) + 2p_2(q_2 - u_{j2}(t))$
  and $c = (q_1 - u_{j1}(t))^2 + (q_2 - u_{j2}(t))^2$

@@

  \clearpage
  %%%%%%%%%%%%%%%% Analytical attempt to integration %%%%%%%%%%%%%%%%%%%%%
\end{comment}

>>>>

  \section{Uncertainty addition in measurement}
  Consider that we have a set of measurements whose mean and variance are known $\mu = E(x)$ and $\Sigma = E ((x - \mu_x)(x - \mu_x)^\top)$. We want to know the
  affect of uncertainty on mean and variance of existing observations. On adding
  noise $[\Delta x, \Delta y]^\top$ with zero mean and covariance $\Delta
  \Sigma = E(\Delta x \Delta x^\top)$ the covariance of new data is given by
  \begin{multline}
    E((x + \Delta x)(x+\Delta x)^\top) = E(xx^\top) + E(x \Delta x^\top) \\
    + E(\Delta x x^\top) + E(\Delta x \Delta x^\top)
  \end{multline}
  where the terms $E(x \Delta x^\top)$ denote the correlation between the data
  vector and the uncertainty in the data. Although we understand that in our case
  the data is the appearance based detection score and uncertainty because of
  occlusion is closely related to the appearance and hence detection score, we
  assume independence between $x$ and $\Delta x$. Hence our resultant covariance
  matrix $ E((x + \Delta x)(x+\Delta x)^\top) = \Sigma + \Delta \Sigma$
  are 4D. But that should not be a problem because the detection scores are
  modeled as $[x_{\text{min}}, y_{\text{min}}, x_{\text{max}},
  y_{\text{max}}]^\top$, we can stack the vectors in the soft occlusion region
  domain as the regions are independent of min or max variation. The parameters
  of 4D occlusion distribution are given by

@@

  With our
  discussion so far, the function $O_{ij}(.)$ gives an additional measure of
  uncertainty associated with each point in the space.

@@

\section{Analytical attempt to integration}
  %%%%%%%%%%%%%%%% Analytical attempt to integration %%%%%%%%%%%%%%%%%%%%%
  \begin{align}
    E^i_{\text{reproj}}(\lambda) &= \left\|\trackpj{t} - \frac{p_{1:2}\lambda +
  q_{1:2}}{p_3\lambda + q_3}\right\|^2\\
  &= \frac{(p_1\lambda + q_1 - u_{j1}(t))^2 + (p_2\lambda + q_2 - u_{j2}(t))^2}
  {(p_3\lambda + q_3)^2}\\
  &= \frac{a\lambda^2 + b\lambda + c}{(p_3\lambda + q_3)^2}
  \end{align}
  where $a = p_1^2 + p_2^2$, $b = 2p_1(q_1 - u_{j1}(t)) + 2p_2(q_2 - u_{j2}(t))$
  and $c = (q_1 - u_{j1}(t))^2 + (q_2 - u_{j2}(t))^2$

@@

  \clearpage
  %%%%%%%%%%%%%%%% Analytical attempt to integration %%%%%%%%%%%%%%%%%%%%%
